\documentclass{article}

\usepackage[a4paper]{geometry}
\usepackage{tabularx}
\usepackage{CV}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{}

\fancyhead[L]{Sean Robertson}
\fancyhead[R]{\thepage / \pageref{LastPage}}

\begin{document}

\thispagestyle{empty}

\begin{center}
  \huge{Sean Robertson}
\end{center}
\vspace{\baselineskip}

\begin{center}
  \begin{minipage}{0.5\textwidth}
  \begin{flushleft}
    D.L. Pratt Building, \\
    6 King's College Rd., Rm. 265C, \\
    Toronto, ON, M5S 3H5
  \end{flushleft}
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\textwidth}
  \begin{flushright}
    +1 (647) 701 6206 \\
    \href{mailto:sdrobert@cs.toronto.edu}{sdrobert@cs.toronto.edu} \\
    \href{https://sdrobert.github.io}{sdrobert.github.io}
  \end{flushright}
  \end{minipage}
\end{center}

\section{Education}
\begin{CV}
  \item[2022-pres] Postdoctoral Fellow,
    \href{https://www.utoronto.ca/}{University of Toronto}, Canada

  \item[2016-2023] PhD Computer Science, University of Toronto, Canada
    
  \item[2013-2015] MSc Computer Science, University of Toronto, Canada

  \item[2008-2013] Bachelor of Computer Science, Minor in Psychology, Hons.,
    Co-op, \href{https://uwaterloo.ca/}{University of Waterloo}, Canada
\end{CV}

\section{Honours}
\begin{CV}

  \item[2023-pres] Faculty Affiliate Researcher, Vector Institute
  
  \item[2022-pres] \href{https://datasciences.utoronto.ca/postdoctoral-fellows/}
    {Postdoctoral Fellowship}, Data Sciences Institute (DSI)

  \item[2018-2019,2021-2022] \href{https://vectorinstitute.ai/2021/03/31/vector-welcomes-new-researchers-to-postgraduate-affiliate-program/}
    {Postgraduate Affiliation}, Vector Institute

  \item[2017-2020] \href{http://www.nserc-crsng.gc.ca/Students-Etudiants/PG-CS/BellandPostgrad-BelletSuperieures_eng.asp}
    {Canadian Graduate Scholarship - Doctoral (CGS-D)}, Natural Sciences and
    Engineering Research Council of Canada (NSERC)

  \item[2016] \href{https://osap.gov.on.ca/OSAPPortal/en/A-ZListofAid/PRDR013089.html}
    {Ontario Graduate Scholarship}, Government of Ontario and the University of
    Toronto

  \item[2014-2015] \href{http://www.nserc-crsng.gc.ca/Students-Etudiants/PG-CS/CGSM-BESCM_eng.asp}
    {Canadian Graduate Scholarship - Master's (CGS-M)}, Natural Sciences and
    Engineering Research Council of Canada (NSERC)

  \item[2013-2015] \href{http://www.artsci.utoronto.ca/graduate/scholarships-awards/scholarships-by-department/computer-science}
    {Wolfond Scholarship Program for Wireless Information Technology},
    University of Toronto

  \item[2011-2012] \href{http://www.nserc-crsng.gc.ca/Students-Etudiants/UG-PC/USRA-BRPC_eng.asp}
    {Undergraduate Student Research Award}, NSERC

\end{CV}

\section{Research Interests and Experience}
\begin{CV}
  \item[Current] Topics: Accent-robust speech recognition; ASR pre-training;
    low-resource ASR; evaluation.

  \item[PhD] Topics: Speech recognition; deep learning; multi-scale
    speech processing; digital signal processing; reinforcement learning;
    variational inference.

    Courses taken: Spoken Language Processing (A+);
    Information Visualization (A+);
    Learning Discrete Latent Structure (A+);
    and Numerical Methods for Optimization Problems (A+).

  \item[Master's] Topics: Computer-assisted pronunciation training;
    phonology; pedagogy; machine learning; experimental design; experimental
    statistics; and mobile human-computer interaction.

    Courses taken: Fundamentals of Cryptography (A+); Natural Language
    Computing (A+); Human-Computer Interaction (A+); and Computational
    Linguistics (A+).

  \item[Undergraduate] Research assistantships topics: probabilistic modeling;
    basic (``maker'') circuit board design; digital signal processing; and
    concurrent database scaling.

\end{CV}

\section{Refereed Full Papers and Conference Proceedings}
\begin{itemize}
  \item \textbf{Robertson, S.,} Munteanu, C., Penn, G. (2020).
    \textit{FAB: The French Absolute Beginner Corpus for Pronunciation
    Training}. Language Resources and Evaluation Conference (LREC). 6613-6620

  \item \textbf{Robertson, S.,} Penn, G., Wang, Y. (2019).
    \textit{Improving Speech Recognition with Drop-in Replacements for f-bank
    Features}. Conference on Statistical Language And Speech Processing
    (SLSP). 210-222

  \item \textbf{Robertson, S.,} Munteanu, C., Penn, G. (2018).
    \textit{Designing Pronunciation Learning Tools: The Case for Interactivity
    against Over-Engineering}. Conference on Human Factors in Computing Systems
    (CHI). 356:1-356:13.

  \item \textbf{Robertson, S.,} Munteanu, C., Penn, G. (2016).
    \textit{Pronunciation Error Detection for New Language Learners}.
    Interspeech, 2691-2695.

  \item Rudzicz, F., Frydenlund, A., \textbf{Robertson, S.,} Thaine, P. (2016).
    \textit{Acoustic-Articulatory Relationships and Inversion in Sum-Product
    and Deep-Belief Networks}. Speech Communication, 79, 61-73.
\end{itemize}

\section{Workshop Proceedings and Non-Refereed Papers}
\begin{itemize}
  \item \textbf{Robertson, S.} and Dunbar, E. (2023) \textit{Bigger is not
    Always Better: The Effect of Context Size on Speech Pre-Training}. arXiv
    preprint, \texttt{arXiv:2312.01515}

  \item \textbf{Robertson, S.,} Penn, G., Wang, Y. (2019) \textit{Exploring
    Spectro-Temporal Features in End-to-End Convolutional Neural Networks}.
    arXiv preprint, \texttt{arXiv:1901.00072}.

  \item \textbf{Robertson, S.,} Munteanu, C., Penn, G. (2016).
    \textit{Language Learning Dialogue systems: Lessons in Proving Yourself}.
    Designing Speech and Multimodal Interactions for Mobile, Wearable, and
    Pervasive Applications, CHI.

  \item Minhas, U. F., Liu, R., Aboulnaga, A., Salem, K., Ng, J.,
    \textbf{Robertson, S.} (2012). \textit{Elastic Scale-Out for
    Partition-Based Database Systems}. IEEE 28th International Conference on
    Data Engineering Workshops (ICDEW), 281-288.
\end{itemize}


\section{Teaching Experience}
\begin{CV}
  
  \item[2014,2016-2019,2021-2022] Computational Linguistics - Teaching Assistant

    Pre- and post-assignment tutorials; assignment revisions; marking;
    occasional stand-in teaching.

  \item[2022] Spoken Language Processing - Teaching Assistant

    Aided graduate students in research project formulation and evaluated their
    outcomes.

  \item[2020,2021] Natural Language Computing - Co-instructor

    Co-taught alongside Frank Rudzicz in both years, and with Serena Jeblee in
    the latter. In addition to lectures and managing TAs, rewrote whole
    assignment and some of the lecture content.

  \item[2014,2017] Introduction to Computer Science - Teaching Assistant

    Overseeing first-year labs.

\end{CV}

\section{Professional Experience}

\begin{CV}
  \item[2022] Vector Institute Conversational AI Project Teaching Assistant.
  \item[2020] AI engineer for Sun Life Financial.
  \item[2014-2018] Contracted work for Speax Inc.
\end{CV}

\section{Service}

\begin{itemize}
  \item Reviews for Journals:%
    \textit{Speech Communication} (2018-2019, 2021-2022)
  \item Reviews for Conferences:%
    \textit{CHI} (2024),%
    \textit{CoNLL} (2023),%
    \textit{AISTATS} (2022-2024),%
    \textit{ICMI} (2021, 2022 - \href{https://icmi.acm.org/2022/awards/}{Best Reviewer Award}),%
    \textit{INTERSPEECH} (2021-2023),%
    \textit{UIST} (2021),%
    \textit{CUI} (2021),%
    \textit{EMNLP} (2019),%
    \textit{CHI - LBW} (2018)%
\end{itemize}

\section{References}

\begin{itemize}
  \item Prof. Gerald Penn (current and past supervisor), Department of
    Computer Science, University of Toronto.
    \href{mailto:gpenn@cs.toronto.edu}{gpenn@cs.toronto.edu}
  \item Prof. Frank Rudzicz (committee member and CSC401 co-instructor),
    Department of Computer Science, University of Toronto.
    \href{mailto:frank@spoclab.com}{frank@spoclab.com}
  \item Prof. Cosmin Munteanu (past supervisor), Department of Computer Science,
    University of Toronto. \href{mailto:cosmin@taglab.ca}{cosmin@taglab.ca}
\end{itemize}

\end{document}
